Workplan

### 2018-04-22 Workplan/Workplan.tex
added Qualifying Report

	\subsection{Presidents Speeches}

@@

	\subsection{January 2019}
	Friday 18th January - Complete first rough pass of capturing and processing speech.

>>>>

	\subsection{Presidents Speeches}
	Data to be downloaded

	\subsection{Experimental Design}
	Battery of tests to differentiate between Controls, those with MCI, those with AD. 
	\begin{itemize}
		\item FCSRDT - As most effective 
	\end{itemize}

@@

	\subsection{October 2018}

	\subsection{November 2018}

	\subsection{December 2018}

	\subsection{January 2019}
	Friday 11th January - Rough Draft of Qualifying Due
	Friday 18th January - Complete first rough pass of capturing and processing speech.
